Figures and Tables

### 2021-01-15 paper/figures_tables.Rmd
Trying a different layout

```{r eval = FALSE,  fig.width=3}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

>>>>

### Figure x.
Distribution of dispersal distances produced by each of the simulation models considered.
```{r fig.width=3}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

```{r fig.width=6, fig.height=3}
plot_grid(a,b, ncol = 2)
```
